---
title: "AnalyseExplo"
author: "Berry et Lemeilleur"
date: "2022-10-05"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---
## R markdown
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Vectors

1.1 Let's start simple

Create the following vectors e1, e2, e3, e4

```{r}
e1 = c(2, 5, 0, 8)
e2 = seq(1, 200, by=1)
e3 = seq(-200, -210, by=-2)
e4= c(2, 4, 8, 16, 32, 64, 128)
```

• Create the vector v of 50 elements with conditions

Nous avons trouvé deux solutions pour cette question, voici la première
(plus complexe) :

```{r}
v <- rep(1,50)
for (i in 1:50)
  if (i %% 2 == 0)
    v[i] = -1 
```

et la seconde qui utilise les puissances de moins 1 :

```{r}
v <- c(-(-1)^(1:50))
```

• Create the vector e5 = (1, 2, ...210) by concatenating e2 and e3.

```{r}
e5 = c(e2,e3)
```

• Read seq's help vignette: ?seq C'est fait!

• Create the vector e7 containing 70 equally spaced values between 0 and
1.

```{r}
e6 = seq(0, 1, length.out = 70)
```

• Create the vector e7 containing 10 times the sequence e1. Tip: use
rep.

```{r}
e7 = rep (e1,10)
```

• What is the result of the operation e2 moins e3 ? This is called
recycling, and this is dangerous.

```{r}
e2-e3
```

1.2 Character vectors 
• Create a vector vowels containing all vowels
```{r}
vowels = c('a', 'e', 'i', 'o', 'u', 'y')
```
•letters is a character vector containing all the letters in alphabetical order. 
```{r}
letters 
```
• What does letters %in% vowels do ? 
```{r}
letters %in% vowels 
```
Pour chaque element de letters si cet element est egalement dans vowels ça renvoie true, et ça renvoie false si cet element n'est pas dans vowels

• Extract the number of each vowel. Tip: use which 
```{r}
which(letters%in% vowels)
```

• Extract the number of each nonvowel 
```{r}
x <- letters[! letters %in% vowels]
for (i in x)
  which(letters==letters[i])
```

Moyen plus simple de le faire (sans boucle) : 
```{r}
which(! letters%in% vowels)
```

• What are the letters right after a vowel ? 
```{r}
letters[which(letters%in% vowels) + 1]

```
• Create the string myname containing
your name (in lower case) 
```{r}
myname = "clemence"
```
• Use strsplit to extract individual letters
of your name. Observe that strsplit returns a list. Access its first
element. 
!!!! A Revoir !!!!
```{r}
namelet = strsplit(myname,"")[[1]]
```
• Give for each character of your name its number in the
alphabet. 
```{r}
which(letters %in% namelet)
```
• Do the same with your right neighbor's name. • Who is on
average lower in the alphabet ?
```{r}
myname2 = "oriane"
namelet2 = strsplit(myname2,"")[[1]]
indics1 = which(letters %in% namelet2)
indics2 = which(letters %in% namelet)
sum(indics1)/length(indics1)
sum(indics2)/length(indics2)


```





\## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to
prevent printing of the R code that generated the plot.
