---
title: "TP2"
output: pdf_document
date: "2022-10-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plots and Given Names

We red the prenoms.csv doc and we plot these information:
– The number of births by year: 

```{r}
library(tidyverse)
date <- read.csv("prenoms.csv",header=TRUE)
```
– The number of births by year: 
```{r}
annee <- date %>% group_by(Année) %>%
  summarise(nbr = sum(Nombre))
ggplot(annee,aes(Année,nbr))+geom_point()
```
– The number of male/female births by year
```{r}
tri2 <- date %>% group_by(Année, Sexe) %>%
  summarise(nbr=sum(Nombre))
ggplot(tri2,aes(Année,nbr,color=Sexe,shape=Sexe))+geom_point()
```
– Is your name in the dataset ?
```{r}
date[date$Prénom == "Clémence",] 
```

– Represent the 10 most given names
```{r}
famous <- date %>% group_by(Prénom) %>%
  summarise(nbr = sum(Nombre))
head(famous[order(-famous$nbr),],10)
```

– Select for each year the top 5 given names by sex and represent their evolution along years.
```{r}
tri4 <- date %>% group_by(Année,Sexe)  %>% 
            mutate(nbr=rank(-Nombre))  %>% 
            filter(nbr<=5 & Sexe=="F") %>%
            ggplot(aes(x=Année,y=Nombre,fill=Prénom))+geom_histogram(stat="identity", position="dodge")
tri4
tri5 <- date %>% group_by(Année,Sexe)  %>% 
            mutate(nbr=rank(-Nombre))  %>% 
            filter(nbr<=5 & Sexe=="M") %>%
            ggplot(aes(x=Année,y=Nombre,fill=Prénom))+geom_histogram(stat="identity", position="dodge")
tri5
```

– Plot the average number of letters by year
```{r}
ave <- date %>% group_by(Année) %>%
  summarize(aveLetters=mean(str_length(Prénom))) 
ave
```
– Plot the average number of vowels by year
```{r}
print(length(grepl(vowels,strsplit(str_to_lower(toString(date$Prénom,to="ASCII//TRANSLIT")),""))))
#ave <- date %>% group_by(Année) %>%
#  summarize(aveLetters=mean(str_length(grepl(vowels,Prénom))))
#ave
#prenlen <- date %>% group_by(Année) %>%
 # summarize(nbr = length(Prénom))
#prenlen 
  
  
  #pren <- strsplit(str_to_lower(toString(date$Prénom,to="ASCII//TRANSLIT")),"")
#print(which(pren[[1]] %in% vowels))
#vow <- date %>% group_by(Année) %>%
 # summarize(aveVow=length((pren[[1]][pren[[1]] %in% vowels])))
#print(length(grepl(vowels,pren[[1]])))
#print(length((pren[[1]][pren[[1]] %in% vowels])))
#vow
```
  - Plot the average number of consonants by year
```{r}
cons <- date %>% group_by(Année) %>%
  summarize(aveVow=mean(length(which(c(grepl(setdiff(letters,vowels),Prénom)))))) 
cons
```

– How the number of composed names (like Jean-Baptiste or Lou-Ann)


– Define a “hype” criteria and find the hypest names





























```{r}
library(ggpubr)
library(factoextra)
cloud <- read.csv("datacloud.csv",header=TRUE)
data <- (data.frame(cloud)[,-4])
moy <- mean(cloud$cluster)
res <- kmeans(data,2)
fviz_cluster(res,data,ellipse.type = "norm")
```

